Aa Language Reference Manual

### 2010-07-12 Ahir-asm/antlr2/docs/AaLRM.tex
some modifications to the program structure to prepare for the following 1. cycle check in call graph 2. type propagation Added a BGL wrapper class to get dfs functionality...

The rules for scoping are as follows:
\begin{enumerate}
\item A variable (declared or implicit) defined in a scope is visible
in all descendant scopes.
\item A reference to a variable $b$ in a scope X is resolved by checking
whether the variable is defined in that scope, and if not found there,
by checking in the scope that contains the scope X, and so on.
\item A scope can read from variables that are defined in descendant
scopes.  
\item A scope can read from variables that are defined in ancestor scopes.
\end{enumerate}

A variable which is to be read in a statement may be specified 
as follows
\begin{verbatim}
a            look for variable a in current scope; 
             if not found look in the parent.

@@

^:a          look for variable a defined in the parent of
             the current scope.

%p:a         look for variable a defined in the child scope 
	     with label p (child scope of the current scope).

^^:a         look for variable a defined in the parent of
             the parent of the current scope.

%p%q:a       look for variable a defined in the child scope 
             with label q of the child scope with label p of 
             the current scope

a[10]        look for a storage variable a defined in the 
             current module.  If not found, look for it in
             the program scope.  If found in either of the places,
             access the corresponding element of the array.
\end{verbatim}
Thus, a generic variable reference has the form 
\begin{verbatim} 
    scope-id : variable-reference 
\end{verbatim} 
and the scoping rules forbid a scope from accessing variables
which are not defined in either an ancestor or a descendant
of the scope.

@@

           // combine results from parallel statement above
           snontriv := (%parsum%sb1:s  + %parsum%sb2:s)
           $place [nontrivsum]
      $else

           // summation is trivial 
           striv := mem[low]
           $place [trivsum]
      $endif
      $merge nontrivsum trivsum
         // which sum do you pick? depends on which path was taken
         $phi sum := snontriv $on nontrivsum strivsum $on trivsum
      $endmerge
    }

    // bring sum up to the surface.
    sum := %trivcheck:sum
}
\end{verbatim}
This example describes an algorithm which computes the sum of
a section of an array by dividing the problem into two partial
summations.

>>>>

The rules for scoping are as follows:
\begin{enumerate}
\item A declared variable defined in a scope is visible
in all descendant scopes. In addition
\begin{itemize}
\item If $x$ is a storage or pipe variable defined in a scope, then
there can be no other variable named $x$ in any of the scopes
contained in this scope.
\item If $x$ is an input or output argument of a module, then
there can be no other variable named $x$ declared in any of
the descendant scopes of this module.
\end{itemize}
\item A reference to a variable $b$ in a scope X is resolved by checking
whether the variable is defined in that scope, and if not found there,
by checking in the scope that contains the scope X, and so on.
\item A scope can read from variables that are defined in descendant
scopes.  
\item A scope can read from variables that are defined in ancestor scopes.
\item A scope can only write to one of the following:
\begin{itemize}
\item a storage or pipe variable defined in the scope or an ancestor
of the scope.
\item an output argument of a module of which the scope is a descendant.
In this case, there can be at most one statement in the entire module
which writes to this output argument.
\end{itemize}
\end{enumerate}

A variable reference in a statement may be specified 
as follows
\begin{verbatim}
a            look for variable a in current scope; 
             if not found look in the parent.

@@

^:a          look for variable a starting from the parent of
             the current scope.

%p:a         look for variable a starting from the child scope 
	     with label p (child scope of the current scope).

^^:a         look for variable starting from the parent of
             the parent of the current scope.

%p%q:a       look for variable starting from the child scope 
             with label q of the child scope with label p of 
             the current scope

a[10]        look for a storage variable a defined in the 
             current scope.  If not found, look for it in
             the parent scope, and so on.  If eventually found, 
             access the corresponding element of the array.
\end{verbatim}
Thus, a generic variable reference has the form 
\begin{verbatim} 
    scope-id : variable-reference 
\end{verbatim} 
and the scoping rules forbid a scope from accessing variables
which are not defined in either an ancestor or a descendant
of the scope.

@@

           // combine results from parallel statement above
           snontriv := (%parsum%sb1:s  + %parsum%sb2:s)
           // put token in place nontrivsum.  It will be picked
           // up by succeeding merge
           $place [nontrivsum]
      $else

           // summation is trivial 
           striv := mem[low]
           // put token in place trivsum.  It will be picked
           // up by succeeding merge
           $place [trivsum]
      $endif
      $merge nontrivsum trivsum
         // which sum do you pick? depends on which path was taken
         // note that sum here refers to the output argument of 
         // the parent module which is globally visible, but can
         // be written into exactly once!
         $phi sum := snontriv $on nontrivsum striv $on trivsum
      $endmerge
    }

}
\end{verbatim}
This example describes an algorithm which computes the sum of
a section of an array by dividing the problem into two partial
summations.
